---
title: "MyDataProductPresentation"
author: "Anita Gaikwad"
date: "12 September 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My Title
**Predict Horse Power from MPG**


Purpose

The purpose of this Shiny app is to predict miles per gallon of a given car model based on its horsepower data. This data is part of the "mtcars" dataset from R's automatically loaded Datasets Package. The source is:

Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.


## "mtcars" Dataset Summary
The dataset consists of 32 observations (different makes/models) with 11 variables. Below is a summary of the dataset.
```{r cars, echo = TRUE}
summary(mtcars)

```

##Static Plot with two models

The dependent variable is the car's horsepower, and the independent variable is the car's miles per gallon (mpg). There are two different models. Model 1 is a simple linear regression. Model 2 is a piecewise regression consisting of two simple linear regressions for the data with mpg < 20, and the data with mpg >= 20. 

```{r}
library(ggplot2)
plot(mtcars$mpg, mtcars$hp, xlab = "miles per gallon", ylab = "horsepower", bty = "n", pch = 16,
       xlim = c(10,35), ylim = c(50,350))
```

## 
Plot URL

The application allows the user to view the plot, and predict the horsepower using the two models by inputting a given mpg by using a slider widget. The running application can be found at this URL:

https://alemarc21.shinyapps.io/week4proj/


